\subsection{{\tt mdap\_get\_2d\_map.pro}}
\label{dap_sec:mdap_get_2d_map}

This module is responsable to arrange the outputs of
mdap\_spectral\_fitting.pro into a two-dimensional map, given some
spatial binning informations. 

Table \ref{dap_tab:mdap_get_2d_map} lists the inputs and
outputs required for this module.



\begin{center}
\begin{longtable}{p{2.7cm}| p{11.1cm}}
\caption{Inputs and outputs parameters of mdap\_get\_2d\_map.pro} \label{dap_tab:mdap_get_2d_map} \\
\hline
\endfirsthead
\hline
\endhead
\hline
\endlastfoot
\hline
{\bf  INPUTS} &  \\
%
values   &   [Nbins elements dbl array].  Measured quantity for each spatial bin (first elements is associated with bin 0 , 
            second element with bin 1, and soforth). It can be either an output of block 4 or block 5. \\
%
binning  &   [N x M dbl array]. Two dimensional map showing the binning sheme. Pixels beloning to the i+1-th 
                               bin have value i (i= 0, 1, ..., Nbins-1). Pixels associated to no spatial bin
                               have value -1 (produced in block 2 by mdap\_spatial\_binning.pro). Nbins is the number of spatial bins. \\
%
x2d      & [N x M flt array].  X coordinates of the field of view, in arcsec (produced in block 1 by mdap\_read\_datacube.pro). Coordinate 0 is the center of the field of view.\\
%
y2d      & [N x M flt array].  Y coordinates of the field of view, in arcsec (produced in block 1 by mdap\_read\_datacube.pro). Coordinate 0 is the center of the field of view.\\
%
\hline
{\bf OUTPOUTS}        &    \\
%
map      & [N x M flt array].  Measured values over the two-dimensional field of view. Pixels belonging to the same spatial bin 
                               have the same value (i.e. no spatial smoothing or interpolation are performed). \\
\hline
\end{longtable}
\end{center}

