\subsection{{\tt mdap\_measure\_indices.pro}}
\label{dap_sec:mdap_measure_indices}

This interface is responsible for measuring the strength of the
absoprtion line indices, their errors, and correct them for galaxy
intrinsic broadening. Broadening correction is applied to the input
galaxy spectra to match the spectral resolution of the spectral
indices system (e.g. Lick). Input galaxy spectra must have emission
lines removed.

The measurement of the index is performed by the main module
mdap\_do\_measure\_indices.pro, see Section
\ref{dap_sec:mdap_do_measure_indices}.

Warning: ``D4000'' and ``TiO0p89'' (i.e. TiO0.89) indices are defined
as the ratio of the flux in the red and blue pseudocontinua. This
alternative configuration is hardwired in the
mdap\_measure\_indices.pro interface, and it is triggered by the index
name (i.e. be sure that the user input file with indices definitions
have these two names correcty spelled).

Broadening correction is done according to the following formula

\[
I_{\rm corr} = I_{\rm gal} \frac{I_{\rm templ}}{I_{\rm templ\ LOSVD}}
\]
for atomic indices, and 
\[
I_{\rm corr} = I_{\rm gal} + I_{\rm templ} - I_{\rm templ\ LOSVD}
\]
for molecular indices.  $I_{\rm corr}$ is the index line strength
corrected for intrinsic broadening, $I_{\rm templ}$ is the index line
strength measured on the best fitting stellar template, and $I_{\rm
  templ\ LOSVD}$ is the index line strength measured on the best
fitting stellar template convolved by the best fitting LOSVD.

The Convolution the input spectra to match a desired system is done by
the utility module mdap\_convol\_sigma (Section
\ref{dap_sec:mdap_convol_sigma}).

The list of input/output parameters for this module is given in Table
\ref{dap_tab:mdap_measure_indices}.


\begin{center}
\begin{longtable}{p{2.7cm}| p{11.1cm}}
\caption{Inputs and outputs parameters of mdap\_measure\_indices.pro} \label{dap_tab:mdap_measure_indices} \\
\hline
\endfirsthead
\hline
\endhead
\hline
\endlastfoot
\hline
{\bf  INPUTS} & \\
\hline
wavelength & [N elements array]. Vector containing the wavelenghts of the input spectra. The dispersion can be also not constant.\\
%
spectra & [T x N elements array].  Vector containing the T input galaxy spextra, with emission line removed. Spectra are defined over the vector wavelength.\\
%
best\_template & [T x N elements array]. Vector containing the T best fitting stellar templates obtained when fitting the kinematics of the input spectra. 
                Spectra are defined over the vector wavelength.\\
%
best\_template\_ LOSVD, & [T x N elements array]. Vector containing the T best fitting stellar templates, convolved with the best-fitting stellar LOSVD, obtained when 
                  fitting the kinematics of the input spectra. Spectra are defined over the vector wavelength. \\
%
stellar\_velocity & [T elements array]. Vector containing the best fitting stellar velocity for the T input spectra in km/sec. P.S. Set it to zero if the input spectra are in rest-frame\\
%
residuals & [T x N elements array]. Vector containing the residuals from the best fit model to the input galaxy spectra. Residuals are defined over the vector wavelength.  \\
%
fwhm\_diff\_ indices\_ & [N elements array]. Vector that specifies the FWHM($\lambda$) (in \AA) that should be used to broaden the spectra, best\_template, and best\_template\_LOSVD to match the spectral resolution of the spectral indices system.\\
\hline 
{\bf OPTIONAL INPUTS} & \\
\hline
dir=dir  &  Directory where to store the ps files showing the measurements \\
%
\hline
{\bf OUTPUTS} & \\
\hline
abs\_line\_ indices & [T x Nind array]. Absorption line indices of the T inut spectra, corrected for intrinsic broadening. The Nind measure indices are defined in 
   aborption\_line\_ indices\_definition, specified in the configuration file (see Section \ref{dap_sec:configuration}).\\
%
abs\_line\_ indices\_errors & [T x Nind array]. Errors associated to abs\_line\_ indices. \\
%
abs\_line\_ indices\_template &  Absorption line indices measured on best\_template \\
%
abs\_line\_ indices\_template\_ losvd &   Absorption line indices measured on best\_template\_ LOSVD.\\
\hline
{\bf  OPTIONAL OUTPUTS} &  \\
\hline
version & string specifying the module version. If requested, the module is not execute and only version flag is returned.\\
\hline
\hline
\end{longtable}
\end{center}



