\subsection{{\tt mdap\_create\_starting\_guesses.pro}}
\label{dap_sec:mdap_create_starting_guesses}


This interface is responsible to transform the kinematics measured on
a spatial binning scheme into starting guesses for the fit of another
spatial binning scheme. The main module that performs the computation
is mdap\_interpolate\_2dmaps.pro (see Section
\ref{dap_sec:mdap_interpolate_2dmaps}). 

Table \ref{dap_tab:mdap_create_starting_guesses} lists the inputs and
outputs of mdap\_create\_starting\_guesses.pro.


\begin{center}
\begin{longtable}{p{2.7cm}| p{11.1cm}}
\caption{Inputs and outputs  parameters of mdap\_create\_starting\_guesses.pro} \label{dap_tab:mdap_create_starting_guesses} \\
\hline
{\bf  INPUTS} & \\
\hline
\endfirsthead
\hline
\endhead
\hline
\endlastfoot
\hline
 input\_map  & Nx4 (or Nx2)  elements array containing the measurements  of velocity, velocity dispersion 
              of the N spectra to be used to get the starting guesses. If the keyword /h3h4 is set, input\_map
              must be Nx4 elements array, and previous measurements of h3 and h4 must be given.

              \medskip

              \ \ \ input\_map[*,0]: previous velocity measurements

              \ \ \ input\_map[*,1]: previous velocity dispersion measurements

              \ \ \ input\_map[*,2]: (optional) previous H3 measurements

              \ \ \ input\_map[*,3]: (optional) previous H4 measurements\\
%
input\_xbin  &  N elements array. X coordinates of the center of the spatial bins where the measurements in input\_map refer to.  \\
%
input\_ybin  &  N elements array. Y coordinates of the center of the spatial bins where the measurements in input\_map refer to.  \\
%
x2d          &  N'xM' elements array. Two dimensional map of X coordinates of a regular grid mapping the full field of view.  \\
%
y2d          &   N'xM' elements array. Two dimensional map of Y coordinates of a regular grid mapping the full field of view.       \\
%
velocity\_initial\_guess   & Float. Guess for the velocity to be used in the case of previous measurements are NaN, or not defined.  \\
%
velocity\_dispersion\_initial\_guess & Float. Guess for the velocity to be used in the case of previous measurements are NaN, or not defined, 
                                    or outside a fiducial interval $21<\sigma<499$ km/sec.     \\
%
H3\_initial\_guess  &  Float. Guess for the velocity to be used in the case of previous measurements are NaN, or not defined, or outside a fiducial
                          interval $-0.399 < h3 < 0.399$.  \\
%
H4\_initial\_guess  &  Float. Guess for the velocity to be used in the case of previous measurements are NaN, or not defined, or outside a fiducial
                          interval $-0.399 < h4 < 0.399$.  \\ 
%
output\_xbin &  M elements array. X coordinates of the center of the spatial bins where the starting guesses are to be computed. \\
%
output\_ybin & M elements array. Y coordinates of the center of the spatial bins where the starting guesses are to be computed. \\
\hline
{\bf  KEYWORD} & \\
\hline
/h3h4    &   If set, the guesses of Gauss Hermite moments (h3, h4) will be computed (otherwise set to H3\_initial\_guess and
             H4\_initial\_guess) . The input input\_map must contain h3 and h4 measurements.     \\
\hline
{\bf  OUTPUTS} & \\
\hline
output\_start\_guess &   Mx4 elements array containing the interpolated velues of of velocity, velocity dispersion of the N spectra 
             to be used as starting guesses. If the keyword /h3h4 is set, it will be Mx4 elements array.

      \medskip

   \  \  \                output\_start\_guess[*,0]: velocity interpolated on the  output\_xbin, output\_ybin, grid to be used as starting guesses.

   \  \  \           output\_start\_guess[*,1]: velocity dispersion interpolated on the  output\_xbin, output\_ybin, grid to be used as starting guesses.

   \  \  \            output\_start\_guess[*,2]: (optional) H3 interpolated on the  output\_xbin, output\_ybin, grid to be used as starting guesses.

   \  \  \            output\_start\_guess[*,3]: (optional) H4 interpolated on the  output\_xbin, output\_ybin, grid to be used as starting guesses.\\

\hline
\end{longtable}
\end{center}
